Efficient Thresholded Correlation using Truncated Singular Value Decomposition

### 2015-07-22 threshold/draft.Rnw
Added a few more related citations;need to work this in to the intro

XXX add discussion of applications (genomics?) and previous work,
then on to the preliminaries:
\[\]

@@

Let $a_i$ and $a_j$, $1\le i,j\le n$ be any two columns of the matrix $A$
(including possibly the case $i=j$). Denote the correlation of these two vectors
by $\mathrm{cor}(a_i,a_j) = a_j^T a_i$.  The following simple lemma
from Rafiei\cite{raf} establishes a relationship between correlation and
Euclidean distance between two vectors.

@@

%% XXX switch to bibtex

\begin{thebibliography}{99}
\bibitem{br}
Baglama, J. and Reichel, L., Augmented Implicitly Restarted Lanczos Bidiagonalization Methods, SIAM J. Sci. Comput. 2005.
\bibitem{mnl}
Mueen, A., Nath, S., and Liu, J., Fast approximate correlation for
massive time-series data, in Proceedings of the 2010 ACM SIGMOD International
Conference on Management of data, 2010, pp. 171-182.
\bibitem{raf}
Rafiei, D., On similarity-based queries for time series data,
in Data Engineering Proceedings., IEEE, 1999.
\bibitem{zf}
Zhang, J. and Feigenbaum, J, Finding Highly Correlated Pairs Efficiently with Powerful Pruning,
in Proceedings of ACM Conference on Information and Knowledge Management (CIKM), 2006, pp. 152-161.
\bibitem{irlba-R}
\url{https://cran.r-project.org/web/packages/irlba/index.html}
\bibitem{irlba-P}
\url{https://github.com/bwlewis/irlbpy}
\bibitem{irlba-M}
\url{http://www.math.uri.edu/~jbaglama/software/irlba.m}
\end{thebibliography}
\end{document}

>>>>

XXX add discussion of applications (genomics?) and previous work (in particular
\cite{latj} and \cite{bhpt} are related but different),
then on to the preliminaries:
\[\]

@@

Let $a_i$ and $a_j$, $1\le i,j\le n$ be any two columns of the matrix $A$
(including possibly the case $i=j$). Denote the correlation of these two
vectors by $\mathrm{cor}(a_i,a_j) = a_j^T a_i$.  The following simple lemma
establishes a relationship between correlation and Euclidean distance between
two vectors.

@@

%% XXX switch to bibtex / make citations uniform

\begin{thebibliography}{99}
\bibitem{br}
Baglama, J. and Reichel, L., Augmented Implicitly Restarted Lanczos Bidiagonalization Methods, SIAM J. Sci. Comput., 2005.
\bibitem{bhpt}
Bair, E., Hastie, T., Paul, D.., and Tibshirani, P., Prediction by supervised principal components, Journal of the American Statistical Association 101, no. 473, 2006.
\bibitem{latj}
Levin, Asriel U., Todd K. Leen, and John E. Moody. Fast pruning using principal components. (1993).
\bibitem{mnl}
Mueen, A., Nath, S., and Liu, J., Fast approximate correlation for
massive time-series data, in Proceedings of the 2010 ACM SIGMOD International
Conference on Management of data, 2010, pp. 171-182.
\bibitem{raf}
Rafiei, D., On similarity-based queries for time series data,
in Data Engineering Proceedings., IEEE, 1999.
\bibitem{zf}
Zhang, J. and Feigenbaum, J, Finding Highly Correlated Pairs Efficiently with Powerful Pruning,
in Proceedings of ACM Conference on Information and Knowledge Management (CIKM), 2006, pp. 152-161.
\bibitem{irlba-R}
\url{https://cran.r-project.org/web/packages/irlba/index.html}
\bibitem{irlba-P}
\url{https://github.com/bwlewis/irlbpy}
\bibitem{irlba-M}
\url{http://www.math.uri.edu/~jbaglama/software/irlba.m}
\end{thebibliography}
\end{document}
